### 2023-03-30 talk/talk.tex
draft of tamu talk
typo

%% ABSTRACT: We consider inference for a collection of partially observed, stochastic, interacting, nonlinear dynamic processes. Each process is called a unit, and our primary motivation arises in biological metapopulation systems where a unit is a spatially distinct sub-population. Block particle filters are an effective tool for simulation-based likelihood evaluation for these systems, which are strongly dependent through time on a single unit and relatively weakly coupled between units. Iterated filtering algorithms can facilitate likelihood maximization for simulation-based filters. We introduce a new iterated block particle filter algorithm applicable to parameters that are either unit-specific or shared between units. We demonstrate this algorithm to carry out inference on a coupled epidemiological model for spatiotemporal measles case report data in twenty towns.

@@

MFO workshop on \\
Design and Analysis of Infectious Disease Studies
\\
Feb 23, 2023

@@

Slides are at \url{https://ionides.github.io/talks/mfo23.pdf}
%% 8:15am EST

@@

      \item IBPF has theoretical guarantees similar to BPF (Ning \& Ionides, {\it arXiv}, 2023).

>>>>

%% ABSTRACT: We consider inference for a collection of partially observed, stochastic, interacting, nonlinear dynamic processes. Each process is called a unit, and our primary motivation arises in biological metapopulation systems where a unit is a spatially distinct sub-population. Block particle filters are an effective tool for simulation-based likelihood evaluation for these systems, which are strongly dependent through time on a single unit and relatively weakly coupled between units. Iterated filtering algorithms can facilitate likelihood maximization for simulation-based filters. We introduce a new iterated block particle filter algorithm applicable to parameters that are either unit-specific or shared between units. We demonstrate this algorithm to carry out inference on a coupled epidemiological model for spatiotemporal measles case report data in twenty towns. We discuss other applications, to cholera in Haiti and COVID-19 in China.

@@

Texas A\&M Statistics Colloquium\\
Apr 21, 2023

@@

Slides are at \url{https://ionides.github.io/talks/tamu23.pdf}

@@

      \item IBPF has theoretical guarantees similar to BPF (Ning \& Ionides, {\it JMLR}, 2023).
